Trajipaq_sentiment_cr

### 2023-06-05 1. Trajipaq_sentiment/2. Codes/Trajipaq_sentiment_cr.Rmd
update

>>>>

# WGI

trajipaq <- as_factor(trajipaq, only_labelled = TRUE)

wgidataset <-
  wgidataset %>%
  mutate(countryname = recode(countryname, 
                              "South Africa" = "Afrique du Sud, République d'",
                              "Albania" = "Albanie",
                              "Algeria" = "Algérie",

                              "Germany" = "Allemagne",
                              "Saudi Arabia" = "Arabie saoudite",
                              "Argentina" = "Argentine",
                              "Armenia" = "Arménie",
                              "Australia" = "Australie",
                              "Belarus" = "Bélarus",
                              "Belgium" = "Belgique",
                              "Benin" = "Bénin",
                              "Brazil" = "Brésil",
                              "Bulgaria" = "Bulgarie",
                              "Cape Verde" = "Cabo Verde",
                              "Cambodia" = "Cambodge",
                              "Cameroon" = "Cameroun",
                              "Central African Republic" = "Centrafricaine, République",
                              "Chile" = "Chili",
                              "China" = "Chine",
                              "Jordan" = "Cisjordanie et bande de Gaza (Palestine)",
                              "Colombia" = "Colombie",
                              "Congo, Dem. Rep." = "Congo, République démocratique du", # ajouter modif sur trajipaq CR 1 wrong
                              "Korea, Rep." = "Corée du sud",
                              "Dominica" = "Dominicaine, République",
                              "Egypt, Arab Rep." = "Égypte",
                              "United Arab Emirates" = "Émirats arabes unis",
                              "Spain" = "Espagne",
                              "United States" = "États-Unis",
                              "Fiji" = "Fidji",
                              "Greece" = "Grèce",
                              "Grenada" = "Grenade",
                              "Haiti" = "Haïti",
                              "Hong Kong SAR, China" = "Hong Kong",
                              "India" = "Inde",
                              "Iran, Islamic Rep." = "Iran",
                              "Israel" = "Israël",
                              "Italy" = "Italie",
                              "Jamaica" = "Jamaïque",
                              "Japan" = "Japon",
                              "Latvia" = "Lettonie",
                              "Lebanon" = "Liban",
                              "Moroco" = "Maroc",
                              "Mauritius" = "Maurice",
                              "Mexico" = "Mexique",
                              "Nigeria" = "Nigéria",
                              "New Zealand" = "Nouvelle-Zélande",
                              "Uganda" = "Ouganda",
                              "Uzbekistan" = "Ouzbékistan",
                              "Papua New Guinea" = "Papouasie-Nouvelle-Guinée",
                              "Netherlands" = "Pays-Bas",
                              "Peru" = "Pérou",
                              "Poland" = "Pologne",
                              "Romania" = "Roumanie",
                              "United Kingdom" = "Royaume-Uni",
                              "Russian Federation" = "Russie, Fédération de",
                              "St. Vincent and the Grenadines" = "Saint-Vincent-et-les Grenadines",
                              "Senegal" = "Sénégal",
                              "Singapore" = "Singapour",
                              "Slovak Republic" = "Slovaquie",
                              "Sweden" = "Suède",
                              "Switzerland" = "Suisse",
                              "Syria" = "Syrie",
                              "Taiwan, China" = "Taïwan",
                              "Chad" = "Tchad",
                              "Tunisia" = "Tunisie",
                              "Venezuela, RB" = "Venezuela",
                              "Vietnam" = "Viet Nam",
                              "Yemen, Rep." = "Yémen"
                              ))

trajipaq <- merge(trajipaq, wgidataset, by.x = c("annee_qc", "Q11"),
                by.y = c("year", "countryname"), all.x = TRUE)
